Unilateral Divorce and the Rise of Informal Cohabitation

### 2020-09-28 mpc.Rnw
latest

\footnotesize 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline 
\\[-1.8ex] & \multicolumn{1}{c}{Full Sample} & \multicolumn{1}{c}{Resident}& \multicolumn{1}{c}{NSFH}& \multicolumn{1}{c}{NSFG} \Writing to file mpc.tex
Processing code chunks with options ...

You can now run (pdf)latex on ‘mpc.tex’
}{c}{(4)}\\ 
\hline \\[-1.8ex] 
\\[-2.2ex] & \multicolumn{4}{c}{Risk of Marriage relative to Cohabitation} \\  
 \hline \\[-1.8ex]
 Unilateral Divorce &  -0.09  &  -0.07  &  -0.12  &  -0.13  \\ 
  & ( 0.04 ) & ( 0.04 ) & ( 0.04 ) & ( 0.11 ) \\  
 \hline \\[-1.8ex]
 Average Relative Risk &  -0.12  &  -0.08  &  -0.2  &  -0.14  \\ 
 \hline \\[-1.8ex]
 \\[-2.2ex] & \multicolumn{4}{c}{Risk of Separation relative to Cohabitation} \\  
 \hline \\[-1.8ex]
 Unilateral Divorce &  -0.04  &  -0.09  &  -0.05  &  -0.06  \\ 
  & ( 0.02 ) & ( 0.02 ) & ( 0.02 ) & ( 0.1 ) \\  
 \hline \\[-1.8ex]
 Average Relative Risk &  -0.06  &  -0.18  &  -0.1  &  -0.06  \\ 
 \hline \\[-1.8ex]
State Fixed effects & Yes & Yes & Yes & Yes \\ 
Year Fixed effects & Yes & Yes & Yes & Yes \\ 
Age Polynomial & Yes & Yes & Yes & Yes \\
Picewise Duration & Yes & Yes & Yes & Yes \\ 
\hline
Observations & \multicolumn{1}{c}{ 138012 } & \multicolumn{1}{c}{ 81920 } & \multicolumn{1}{c}{ 77826 } & \multicolumn{1}{c}{ 60186 } \\ 
\hline
Censored spells(\%) & \multicolumn{1}{c}{ 10.18 } & \multicolumn{1}{c}{ 10.98 } & \multicolumn{1}{c}{ 11.6 } & \multicolumn{1}{c}{ 8.38 } \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}

>>>>

\footnotesize 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline 
\\[-1.8ex] & \multicolumn{1}{c}{Full Sample} & \multicolumn{1}{c}{Resident}& \multicolumn{1}{c}{NSFH}& \multicolumn{1}{c}{NSFG} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
\\[-2.2ex] & \multicolumn{4}{c}{Risk of Marriage relative to Cohabitation} \\  
 \hline \\[-1.8ex]
 Unilateral Divorce &  -0.24  &  -0.25  &  -0.28  &  -0.28  \\ 
  & ( 0.06 ) & ( 0.08 ) & ( 0.09 ) & ( 0.09 ) \\  
 \hline \\[-1.8ex]
 Average Relative Risk &  0.64  &  0.63  &  0.59  &  0.6  \\ 
 \hline \\[-1.8ex]
 \\[-2.2ex] & \multicolumn{4}{c}{Risk of Separation relative to Cohabitation} \\  
 \hline \\[-1.8ex]
 Unilateral Divorce &  -0.19  &  -0.16  &  -0.08  &  -0.24  \\ 
  & ( 0.07 ) & ( 0.06 ) & ( 0.05 ) & ( 0.14 ) \\  
 \hline \\[-1.8ex]
 Average Relative Risk &  0.67  &  0.71  &  0.83  &  0.62  \\ 
 \hline \\[-1.8ex]
State Fixed effects & Yes & Yes & Yes & Yes \\ 
Year Fixed effects & Yes & Yes & Yes & Yes \\ 
Age Polynomial & Yes & Yes & Yes & Yes \\
Picewise Duration & Yes & Yes & Yes & Yes \\ 
\hline
Observations & \multicolumn{1}{c}{ 138012 } & \multicolumn{1}{c}{ 81920 } & \multicolumn{1}{c}{ 77826 } & \multicolumn{1}{c}{ 60186 } \\ 
\hline
Censored spells(\%) & \multicolumn{1}{c}{ 10.18 } & \multicolumn{1}{c}{ 10.98 } & \multicolumn{1}{c}{ 11.6 } & \multicolumn{1}{c}{ 8.38 } \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}

### 2020-09-28 tiktak.tex
latest

@@

\usepackage[utf8]{inputenc} 
\usepackage{graphicx} % support the \includegraphics command and options
\usepackage{epstopdf}
\usepackage[hang]{footmisc}
\usepackage{lipsum}
\usepackage{setspace}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usepackage{caption}
\usepackage{threeparttablex}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}
%%% PACKAGES
\usepackage{placeins}
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
% These packages are all incorporated in the memoir class to one degree or another...
\usepackage{amsmath}
\numberwithin{table}{section}
\usepackage{cases}
\usepackage{graphicx}
%
\usepackage{float}
\usepackage{authblk}
\usepackage{pgfplots}
\usepackage{pdfpages}
\linespread{1.5}
\setlength{\footnotemargin}{4mm}
\usepackage{amssymb} 
\usepackage{tabularx}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\addtolength{\footnotesep}{2mm} % change to 1mm

@@

%Math stuff
\DeclareMathOperator*{\argmax}{arg\,max}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\parskip3mm\parindent0cm
\setlength{\droptitle}{-10em}   % This is your set screw

\title{Unilateral Divorce and the Rise of Informal Cohabitation\thanks{The authors wish to thank Matthias Doepke, Alessandra Voena and the Norhtwestern Macro group for their useful comments. Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on "family transformations").}}
\author{Fabio Blasutto$^1$ (Presenter) \quad Egor Kozlov$^2$}

\begin{document}
	 	\tikzstyle{block} = [draw, fill=white, rectangle, 
	minimum height=3em, minimum width=6em]
	\tikzstyle{sum} = [draw, fill=white, circle, node distance=1cm]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]

	%Gauss distribution
	\pgfmathdeclarefunction{gauss}{2}{%
		\pgfmathparse{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))}%
	}
	% Bibliography style, important for biblatex functioning	
	\bibliographystyle{apa}

	\maketitle

	\footnotetext[1]{IRES, UCLouvain \& National Fund for Scientific Research (Belgium). Email:  \tt{fabio.blasutto@uclouvain.be}, Phone:\tt{+32 489545996}, Address: \tt{Chaussee de Wavre 561/2, Etterbeek, Belgium.}}
	\footnotetext[2]{Northwestern Univrsity. Email:  \tt{egorkozlov2020@u.northwestern.edu}.\\}

\begin{abstract}
	Does unilateral divorce eroded the gains of marriage with respect to informal cohabitation? Exploiting the staggered introduction of unilateral divorce across U.S. states, we show that after the reform newly formed relationships are 5\% more likely to be cohabitations instead of marriages, and that cohabitation spells last longer. To understand the mechanisms underlying the law changes, we build and estimate a structural life cycle model with partnership choice, female labor supply and savings decisions, where the gains of marriage with respect to cohabitation come from a better risk sharing and specialization within the household, enforced through a costly divorce. In the model the reform increases the risk of divorce, making cohabitation preferred to couples that would have had the highest risk of divorce. Since the couples switching relationship are on average better matched than the average cohabitants, the duration of cohabitations increases.
\end{abstract}
\textbf{Keywords}: Marriage, Cohabitation, Unilateral Divorce, Structural Estimation\\
\textbf{JEL-Code}: D83 - J12

>>>>

\usepackage{pgf}

@@

\usepackage[utf8]{inputenc} 
\usepackage{graphicx} % support the \includegraphics command and options
\usepackage{epstopdf}
\usepackage[hang]{footmisc}
\usepackage{lipsum}
\usepackage{setspace}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usepackage{caption}
\usepackage{threeparttablex}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}
%%% PACKAGES
\usepackage{placeins}
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim

% These packages are all incorporated in the memoir class to one degree or another...
\usepackage{amsmath}
\numberwithin{table}{section}
\usepackage{cases}
\usepackage{graphicx}
%
\usepackage{float}
\usepackage{authblk}
\usepackage{pgfplots}
\usepackage{pdfpages}
\linespread{1.5}
\setlength{\footnotemargin}{4mm}
\usepackage{amssymb} 
\usepackage{tabularx}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\addtolength{\footnotesep}{2mm} % change to 1mm

@@

\renewcommand{\thesubfigure}{ (\alph{subfigure})}
\captionsetup[sub]{labelformat=simple}
%Math stuff
\DeclareMathOperator*{\argmax}{arg\,max}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\parskip3mm\parindent0cm

\title{The Rise of Cohabitation and Unilateral Divorce\thanks{The authors wish to thank David de la Croix, Matthias Doepke, Fabio Mariani, Alessandra Voena and the Norhtwestern Macro group for their useful comments. Blasutto acknowledges financial support from the French speaking community of Belgium (ARC project 15/19-063 on \textit{family transformations} and \textit{mandat d' aspirant} FC 23613).}}
\author{Fabio Blasutto$^1$ \quad Egor Kozlov$^2$}

\begin{document}
	\bibliographystyle{apa}
	\section*{TikTak: an efficient Global Optimizer}
	Research by \cite{arnoud2019} compares an array of local and global optimizers, which are given the task of finding the global optimum of non well-behaved functions. They find that a multistart algorithm that they propose, called TikTak, outperforms the others regarding in terms of time required to reach the solution and the probability that the algorithm actually find the right point. TikTak is implemented following the following steps:
	\begin{enumerate}
		\item Determine bounds for each parameter, then draw and evaluate $N$ Sobol points.
		\item Sort the $N$ Sobol points ($s_1$ ,..., $s_N$), with $f(s_1)\le$ ··· $\le f(s_N)$ and keep the first $N^*$ with $N^*<N$. Note that $f()$ is the objective function. We set those numbers such that $N^*/N=0.15.$ Then, set $j=1$.
		\item Set £Then run local searches ($\hat{s}_1$ ,..., $\hat{s}_N$). Call $z^*_j$ the point resulting from the local minimization\footnote{We use the local minimization algorithm provided by \cite{cartis2019}, which is a derivative-free optimization (DFO) for nonlinear Least-Squares (LS) problems. This algorithm is robust to noise, which might arise because of the errors coming from the approximation of continuous problems on a discrete grid.} starting from $\hat{s}_j$. Then, the next starting point will be a convex combination between $\hat{s}_{j+1}$ and the most fit point computed so far through local minimizations $Z_j^*$, defined as $Z^*_j=\min \{z^*_1,...,z^*_j \} $. Formally:
		$$\hat{s}_{j+1}=(1-\theta_j)s_{j+1}+\theta_j Z^*_j, $$
		where
		$$\theta_j=\min \big[\max[0,1,(j/N^*)^\frac{1}{2}],0.995\big]. $$
		\item The global minimum is $Z^*_{N^*}$.
	\end{enumerate}

\bibliographystyle{achicago}
\bibliography{mybibliography}
